---
title: "Assignment_B-1"
author: "Tzu-Yi Lu, "
date: "2021 Nov 02"
output: github_document
---

```{r}
# Load the packages used in this file.
library(dplyr)
library(tidyr)
library(testthat)
library(datateachr)
```

### Exercise 1: Make a Function && Exercise 2: Document your Function

In my **milestones 1~3** submitted to STAT545A, I kept extracting a specific subset from a current dataset. Therefore, I decided to create a function that helps me with extracting a subgroup from the "**vancouver_trees**" dataset.

I named the function "**extract_dat**", which means extracting data. 

```{r}
#' @tilte Extracting a subset for the tree growth analysis
#' @description  This function calculates the tree age of each observation in the input and then extracts a subset from it according to the specified area(s).
#' @params input_data: The imported data for extracting a subset. This parameter should be a data frame.
#' @params chosen_area The areas you want. This parameter should be a string.
#' @params ref_date The reference date for calculating the tree age of each observation. This parameter should be a string. 
#' @return The observations of the input_data located in the "chosen_area". The output will be a data frame.
#' 
extract_dat <- function(input_data,chosen_area,ref_date) {
  if (!is.data.frame(input_data)) {
    stop("The input data is not a data frame. The input data is ", class(input_data))
  }
  if (!is.character(chosen_area)) {
    stop("The chosen_area variable is not a string. The chosen_area is ", class(chosen_area))
  }
  if (!is.character(ref_date)) {
    stop("The ref_date is not a character. The ref_date is ", class(ref_date))
  }
  
  output_data <-input_data %>%
    dplyr::mutate(tree_age = as.numeric(difftime(as.Date(ref_date),date_planted))/365) %>%
    tidyr::drop_na() %>%
    dplyr::filter(neighbourhood_name  %in% chosen_area)
  return(output_data)
  }

```

## Exercise 3: Examples

### Example 1: 
The way which I used in my milestones. I extracted datasets in the **specified 5 areas** every time before I started my tree growth analysis.

```{r}
# Define the areas I need.
chosen_area <- c("ARBUTUS-RIDGE","DUNBAR-SOUTHLANDS","KITSILANO","SHAUGHNESSY","WEST POINT GREY")

# Run the function
VanTreeUBC <- extract_dat(vancouver_trees, chosen_area, "2021-11-02")
head(VanTreeUBC)
```

### Example 2: 

If I want to extract observations located in **"ARBUTUS-RIDGE"** only, and investigate the tree growth condition in **2015-Jan-01**, I can use the function in this way below. The tree age column in the output variable (VanTree_ARB_2015) will be defined as the length with a unit of the year between the planted date of each observation and the specified date (2015-01-01). 

```{r}
VanTree_ARB_2015 <- extract_dat(vancouver_trees, "ARBUTUS-RIDGE", "2015-01-01")
head(VanTree_ARB_2015)
```

### Example 3: 

If I type in more than one date string in the ref_date, an error will occur while running this function.

```{r, error=TRUE}
VanTree_err <- extract_dat(vancouver_trees, "ARBUTUS-RIDGE", c("2021-01-01","2021-11-02"))
```

## Exercise 4: Test the Function

In the tree growth analysis, the tree age (which is computed by the "**extract_dat**" function) is a critical variable.

The datasets with NA value in the tree_age column do not make sense in the following analysis. Therefore, I need to make sure that all the NA values are excluded in this column. Thus, the first test is to check that there is **no NA value in tree_age column**.

Besides, the tree_age column should be a numeric variable for the following analysis. I also checked **the class of the tree_age column**.

Finally, I want to confirm the class of the output variable as a data frame. 

Here I will test the **VanTreeUBC** variable I got in the **Chunk 3**, and check the **tree_age** column in it.


```{r}
chk <- test_that("Check the tree_age column in the subset.", {
  expect_equal(is.na(VanTreeUBC$tree_age), rep(FALSE,length(VanTreeUBC$tree_age)))
  expect_true(is.numeric(VanTreeUBC$tree_age))
  expect_true(is.data.frame(VanTreeUBC))
})
```
