---
title: "Assignment_B-2"
author: "Tzu-Yi Lu, "
date: "2021 Nov 20"
output: github_document
---

Repo contents:
  (v) NAMESPACE
  (v) DESCRIPTION
  (v) README.Rmd (and README.md)
  (v) R/ directory
  (v) tests/ directory
  (v) man/ directory

# Exercise 1: Function(s)
```{r}
## Loading required package: usethis
library(devtools)

## Confirming package version of devtools
packageVersion("devtools") 

## Creating a new package named "ExtractData"
create_package("/Users/ziyi/GoogleDrive_p/My Drive/PhD/1_STAT545/Assignments/functions-tzuyilu/Assignment_B-2/ExtractData")

## Making the "ExtractData" directory also a Git repository
use_git()

## Creating two functions in this package
use_r("TreeAgeCal")
use_r("RegionSel")
use_r("global")

## Rendering my functions
document()
```

# Exercise 2: High-level documentation
```{r}
use_readme_rmd()
devtools::build_readme()

```

# Exercise 3: DESCRIPTION file
```{r}
# Storing data in this package
use_r("vancouver_trees")

# Importing other packages
use_dev_package("dplyr")
use_dev_package("tidyr")
use_dev_package("datateachr")
use_dev_package("magrittr")

# Authorizing a licence
use_mit_license()

# Editing author information manually

```

# Exercise 4: Tests
```{r}
## Adding test functions in the package
use_test("TreeAgeCal")
use_test("RegionSel")
```


# Tidy Submission
1. Increase the version number in the DESCRIPTION file, using semantic versioning conventions. 
2. Tag a release in your GitHub repository corresponding to your submission before the deadline, using the package version as your tag.
3. Grab the URL corresponding to your tagged release, and submit that to canvas.