---
title: "Assignment_B-2"
author: "Tzu-Yi Lu, "
date: "2021 Nov 20"
output: github_document
---

Repo contents check:
  (v) NAMESPACE
  (v) DESCRIPTION
  (v) README.Rmd (and README.md)
  (v) R/ directory
  (v) tests/ directory
  (v) man/ directory

# Exercise 1: Function(s)
```{r}
## Loading required package: usethis
library(devtools)

## Confirming package version of devtools
utils::packageVersion("devtools") 

## Creating a new package named "ExtractData"
usethis::create_package("/Users/ziyi/GoogleDrive_p/My Drive/PhD/1_STAT545/Assignments/functions-tzuyilu/Assignment_B-2/ExtractData")

## Making the "ExtractData" directory also a Git repository
usethis::use_git()

## Creating two functions in this package
usethis::use_r("TmeDifCal")
usethis::use_r("SubGrpSel")
usethis::use_r("OutputSum")
usethis::use_r("global")

## Rendering my functions
document()
```

# Exercise 2: High-level documentation
```{r}
## Creating a README.rmd file
usethis::use_readme_rmd()
## Knitting the README.rmd file to README.md
devtools::build_readme()
```

# Exercise 3: DESCRIPTION file
```{r}
# Storing data in this package (THIS FILE IS FROM "datateachr" PACKAGE)
usethis::use_r("vancouver_trees")

# Importing other packages to ensure package dependencies
usethis::use_dev_package("dplyr")
usethis::use_dev_package("tidyr")
usethis::use_dev_package("datateachr")
usethis::use_dev_package("magrittr")

# Authorizing a licence
usethis::use_mit_license()

# Editing author information manually

```

# Exercise 4: Tests
```{r}
## Adding test functions in the package
usethis::use_test("TmeDifCal")
usethis::use_test("SubGrpSel")
usethis::use_test("OutputSum")

# Running tests
devtools::test()
```


# Tidy Submission
1. Increase the version number in the DESCRIPTION file, using semantic versioning conventions. 
2. Tag a release in your GitHub repository corresponding to your submission before the deadline, using the package version as your tag.
3. Grab the URL corresponding to your tagged release, and submit that to canvas.